Recovery of a deleted deep sequencing data set sheds new light on the early spread of SARS-CoV-2 in Wuhan

### 2021-06-03 paper/paper.tex
Results thru recovery of sequencing data

\subsection{Recovery of deleted sequencing data from the Google cloud} 
As indicated in Figure~\ref{fig:acc_removed}, none of the deleted sequencing runs could be accessed through the SRA's web interface.
In addition, none of the sequencing runs could be accessed using the command-line tools of the SRA toolkit.
For instance, as of June 3, 2020, running the commands \texttt{fastq-dump SRR11313485} or \texttt{vdb-dump SRR11313485} both returned an error message stating ``err: query unauthorized while resolving query within virtual file system module - failed to resolve accession 'SRR11313395'``.

@@

Based on the hypothesis that deletion of sequencing runs by the SRA might not delete files stored on the cloud, I interpolated the cloud URLs for the deleted accessions and tested if they still yielded the SRA files.
This approach was successful; for instance, as of June 3, 2020, going to \url{https://storage.googleapis.com/nih-sequence-read-archive/run/SRR11313485/SRR11313485} downloads the SRA file for accession SRR11313485.
I have digitally archived this URL on the Wayback Machine at \url{https://web.archive.org/web/20210502130820/https://storage.googleapis.com/nih-sequence-read-archive/run/SRR11313485/SRR11313485}.

>>>>

\subsection{Recovery of deleted sequencing data from the Google cloud} 
As indicated in Figure~\ref{fig:acc_removed}, none of the deleted sequencing runs could be accessed through the SRA's web interface.
In addition, none of the sequencing runs could be accessed using the command-line tools of the SRA Toolkit.
For instance, as of June 3, 2020, running the commands \texttt{fastq-dump SRR11313485} or \texttt{vdb-dump SRR11313485} both returned an error message stating ``err: query unauthorized while resolving query within virtual file system module - failed to resolve accession 'SRR11313395'``.

@@

Based on the hypothesis that deletion of sequencing runs by the SRA might not delete files stored on the cloud, I interpolated the cloud URLs for the deleted accessions and tested if they still yielded the SRA files.
This strategy was successful; for instance, as of June 3, 2020, going to \url{https://storage.googleapis.com/nih-sequence-read-archive/run/SRR11313485/SRR11313485} downloads the SRA file for accession SRR11313485.
I have digitally archived this URL on the Wayback Machine at \url{https://web.archive.org/web/20210502130820/https://storage.googleapis.com/nih-sequence-read-archive/run/SRR11313485/SRR11313485}.

I automated this strategy to download the SRA files for 97 of the 99 sequencing runs corresponding to the 34 of 45 early epidemic samples that were SARS-CoV-2 positive, as well as the 16 hospital samples from February (SRA files for SRR11313490 and SRR11313499 were not accessible via the cloud).
These SRA files are available at \url{https://github.com/jbloom/SARS-CoV-2_PRJNA612766/tree/main/results/sra_downloads}.
I used the SRA Toolkit to get the object timestamp (\texttt{vdb-dump -{}-obj\_timestamp}) and time (\texttt{vdb-dump -{}-info}) for each SRA file.
For all files, the object timestamp is February 15, 2020, and the time is March 16, 2020.
Although the SRA Toolkit does not clearly document the definition of these two properties, my \emph{guess} is that the object timestamp may refer to when the SRA file was created from a FASTQ file uploaded to the SRA, and the time may refer to when the accession was made public.

\subsection{The data are sufficient to determine the viral sequence from the start of spike through the end of ORF10 for many samples}
